\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-04-11 ms/ms.Rnw
tested with new tealeaves master

Unlike previous leaf energy models, \tealeaves~ensures that calculations are technically correct by assigning stadard SI units with the R package \pkg{units} \cite{Pebesma_etal_2016}. Every parameter and calculated value must have correctly assigned units. If units are not properly defined, \tealeaves~will produce an error because it is unable to convert values. For speed, there is also a ``unitless'' version that forgoes careful unit checks during calculations. To ensure accuracy, these unitless functions are tested against their counterparts with units using the \pkg{testthat} package \citep{Wickham_2011b}. Other R packages that contributed to \tealeaves~are \pkg{crayon} \citep{Csardi_2017}, \pkg{dplyr} \citep{Wickham_etal_2018}, \pkg{glue} \citep{Hester_2018}, \pkg{furrr} \citep{Vaughan_Dancho_2018}, \pkg{future} \citep{Bengtsson_2018}, \pkg{ggplot} \citep{Wickham_2016}, \pkg{magrittr} \citep{Bache_Wickham_2014}, \pkg{purrr} \citep{Henry_Wickham_2018b}, \pkg{rlang} \citep{Henry_Wickham_2018a}, \pkg{stringr} \citep{Wickham_2018}, \pkg{tidyr} \citep{Wickham_Henry_2018}.

@@

  # Solve for T_leaf
  T_leaf <- tleaf(leaf_par, enviro_par, constants, 
                  quiet = TRUE, unitless = FALSE)

@@

  # Solve for T_leaf over a range of T_air
  T_leaves <- tleaves(leaf_par, enviro_par, constants, 
                      quiet = TRUE, unitless = FALSE)

>>>>

Unlike previous leaf energy models, \tealeaves~ensures that calculations are technically correct by assigning stadard SI units with the R package \pkg{units} \cite{Pebesma_etal_2016}. Every parameter and calculated value must have correctly assigned units. If units are not properly defined, \tealeaves~will produce an error because it is unable to convert values. To ensure accuracy, these unitless functions are tested against their counterparts with units using the \pkg{testthat} package \citep{Wickham_2011b}. Other R packages that contributed to \tealeaves~are \pkg{crayon} \citep{Csardi_2017}, \pkg{dplyr} \citep{Wickham_etal_2018}, \pkg{glue} \citep{Hester_2018}, \pkg{furrr} \citep{Vaughan_Dancho_2018}, \pkg{future} \citep{Bengtsson_2018}, \pkg{ggplot} \citep{Wickham_2016}, \pkg{magrittr} \citep{Bache_Wickham_2014}, \pkg{purrr} \citep{Henry_Wickham_2018b}, \pkg{rlang} \citep{Henry_Wickham_2018a}, \pkg{stringr} \citep{Wickham_2018}, \pkg{tidyr} \citep{Wickham_Henry_2018}.

@@

  # Solve for T_leaf
  T_leaf <- tleaf(leaf_par, enviro_par, constants,
                  quiet = TRUE)

@@

  # Solve for T_leaf over a range of T_air
  T_leaves <- tleaves(leaf_par, enviro_par, constants, 
                      quiet = TRUE)

### 2019-04-11 ms/ms.tex
tested with new tealeaves master

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Default parameter inputs  
>   leaf_par   <- make_leafpar()
>   enviro_par <- make_enviropar()
>   constants  <- make_constants()
>   # Solve for T_leaf
>   T_leaf <- tleaf(leaf_par, enviro_par, constants, 
+                   quiet = TRUE, unitless = FALSE)
> 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Custom parameter inputs
>   leaf_par   <- make_leafpar(
+     replace = list(
+       leafsize = set_units(c(0.0025, 0.025, 0.25), "m")
+       )
+   )
>   enviro_par <- make_enviropar(
+     replace = list(
+       T_air = set_units(seq(275, 310, 5), "K")
+       )
+   )
>   constants  <- make_constants()
>   # Solve for T_leaf over a range of T_air
>   T_leaves <- tleaves(leaf_par, enviro_par, constants, 
+                       quiet = TRUE, unitless = FALSE)
> 
\end{Sinput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Default parameter inputs  
>   leaf_par   <- make_leafpar()
>   enviro_par <- make_enviropar()
>   constants  <- make_constants()
>   # Solve for T_leaf
>   T_leaf <- tleaf(leaf_par, enviro_par, constants,
+                   quiet = TRUE)
> 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Custom parameter inputs
>   leaf_par   <- make_leafpar(
+     replace = list(
+       leafsize = set_units(c(0.0025, 0.025, 0.25), "m")
+       )
+   )
>   enviro_par <- make_enviropar(
+     replace = list(
+       T_air = set_units(seq(275, 310, 5), "K")
+       )
+   )
>   constants  <- make_constants()
>   # Solve for T_leaf over a range of T_air
>   T_leaves <- tleaves(leaf_par, enviro_par, constants, 
+                       quiet = TRUE)
> 
\end{Sinput}
\end{Schunk}
